\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-06-03 paper/jitp_rr_memo/jitp_rr_memo.tex
finished incorporating additional revisions

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments from reviewers is addressed in the order presented in the review. We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

    \textbf{Response}: In the front-end discussion referenced above we provided additional explanation of current/manual data collection methods. We have also added a discussion of the manual content analysis and its downsides in the e-government literature (as well as a footnote about the literature on campaign websites, which uses similar methods and thus faces the same issues) to the end of the literature section. Finally, we revised the conclusion to point specifically to the implications of our contributions. In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.

>>>>

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments from reviewers is addressed in the order presented in the review.  We should note that we are now approximately 300 words over the 5,000 word limit. We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers. Of course, we are happy to trim further if necessary.  We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

    \textbf{Response}: We agree with this critique of our literature discussion, and we have completely revised Section 2 to focus primarily on the methods that have been applied to collecting data from government websites, and to specifically focus on the challenges posed by manual data collection. We also incorporated a footnote about the literature on campaign websites, which uses similar methods and thus faces the same issues. The discussion of mayoral partisanship and government websites has now been shifted down to the point at which we introduce our application. Finally, we revised the conclusion to point specifically to the implications of our contributions. In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.

### 2021-06-03 paper/manuscript_jitp_rr.tex
finished incorporating additional revisions

\vspace{-.2cm}
\section{Politics and Government Website Content} \vspace{-.2cm}

@@

Existing research that analyzes websites \textit{manually} provides an indication of the potential benefits of automated analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. Papers in the e-government literature differ in terms of specific instruments, indices, and items, but they largely follow the same principle: researchers manually visit each website and record whether a feature is present or not \citep{kaylor2001gauging, Urban2002, jeffres2006metropolitan, Armstrong2011, dolson2012explaining, Feeney2017}\footnote{Another literature following a similar approach concerns the websites of politicians and their parties. By and large, researchers in this field also rely on hand-coding \citep{Norris2003,Druckman2009,Druckman2010,Esterling2011}, albeit with some exceptions, who do use targeted scrapers \citep{Therriault2010,cryer2019navigating}.}. This approach is also used by the Rutgers E-Governance Institute, whose survey instrument has influenced the e-government literature at large. \cite{holzer2016digital} have conducted seven studies, between 2003 and 2016, of the largest city's website in each of the world's 100 nations with the most internet users. In each case, evaluators visit each website and manually score it according to 104 items. However, this level of thoroughness comes at a price - \cite{holzer2016digital} name a total of 127 website evaluators in their list of acknowledgements.

This approach is labor-intensive and therefore expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems. Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within the narrow confines of their pre-defined objectives. Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}. In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial resources might struggle to provide a complete understanding of individual websites. Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one. By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.

@@

\section{Data: US Municipal Government Website Text} \vspace{-.2cm}

@@

\vspace{-.2cm}
\section{The Web-to-Text Pipeline} \vspace{-.2cm}
In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents. We address three methodological challenges.  First, though they contain significant amounts of text, websites are not comprised of clean plain text files. Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files. The first step is aimed at extracting clean plain text from this heterogeneous file base. The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is substantively uninformative. Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways. We make a software recommendation for each of these steps and gather most of them in our R package, \texttt{gov2text}. Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling. We will clarify this distinction as we describe steps in our pipeline.

\subsection{Site to Text Conversion}
\subsubsection{File Type Detection}
The format of a file impacts how textual data can be extracted from a document. For the most part, the file type of a document can be correctly determined its extension. However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text. For example, we found thousands of documents that ended in .html, when they were actually PDFs. A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type. We implement this method using the R package \texttt{wand} \citep{wand}.%\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}

@@

The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files. By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript. We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website. We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site. This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.

@@

We further interpret the STM results using the visualizations we present in Figure \ref{fig:demreptop}. In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics. We illustrate the topics that are discussed above.  Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities. This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM. Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities. This represents 40\% of the average proportion of content allocated to a given topic.

>>>>

\vspace{-.2cm}
\section{The study of Government Website Content} \vspace{-.2cm}

@@

Existing research that analyzes government websites \textit{manually} provides an indication of the potential benefits of automated analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. In most research on website content, researchers manually visit each website and record whether a feature is present or not \citep{kaylor2001gauging, Urban2002, jeffres2006metropolitan, Armstrong2011, dolson2012explaining, Feeney2017}\footnote{A related literature concerns the websites of politicians and their parties. By and large, researchers in this field also rely on hand-coding \citep{Norris2003,Druckman2009,Druckman2010,Esterling2011}, albeit with some exceptions, who do use targeted scrapers \citep{Therriault2010,cryer2019navigating}.}. This approach is also used by the Rutgers E-Governance Institute, whose survey instrument has influenced the e-government literature at large. \cite{holzer2016digital} have conducted seven studies, between 2003 and 2016, of the largest city's website in each of the world's 100 nations with the most internet users. In each case, evaluators visit each website and manually score it according to 104 items. However, this level of thoroughness comes at a price---\cite{holzer2016digital} name a total of 127 website evaluators in their list of acknowledgements.

The manual approach is expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems. Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within their pre-defined objectives. Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}. In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial human resources might struggle to provide a complete understanding of individual websites. Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one. By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.

@@

\section{Application: Mayoral Partisanship and \\ U.S. Municipal Government Website Text} \vspace{-.2cm}

@@

\vspace{-.2cm}
\section{The Web-to-Text Pipeline} \vspace{-.2cm}
In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents. We address three methodological challenges.  First, though they contain significant amounts of text, websites are not comprised of clean plain text files. The first step is aimed at extracting clean plain text from this heterogeneous file base. The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is substantively uninformative. Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways. We make a software recommendation for each of these steps and gather most of them in our R package, \texttt{gov2text}. Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling. We will clarify this distinction as we describe steps in our pipeline.

\subsection{Site to Text Conversion}
\subsubsection{File Type Detection}
The format of a file impacts how text can be extracted from a document. For the most part, the file type of a document can be correctly determined by its extension. However, there are exceptions to this. For example, we found thousands of documents that ended in .html, when they were actually PDFs. A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type. We implement this method using the R package \texttt{wand} \citep{wand}.%\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}

@@

The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather website files. By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript. We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website. We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site. This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.

@@

In Figure \ref{fig:demreptop} we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics. We illustrate the topics that are discussed above.  Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities. This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM. Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities. This represents 40\% of the average proportion of content allocated to a given topic.
